---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `convertr`

<!-- badges: start -->
<!-- badges: end -->

The purpose of `convertr` is to automate converting between R scripts, RMarkdown files and Quarto files with, focusing on managing code-chunks, code comments, and the differences in YAML options between .qmd and .rmd files. 

> ⚠️ **Warning**  
> This package is currently under development and may only work as intended in a limited number of situations. As with all R functions that write files, `convertr` will not check for duplicate files and will automatically overwrite files in the output directory if an output file with the name already exists. Test on a back-up copy of your file before using.  


## Installation

You can install the development version of convertr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("martinasladek/convertr")
```

## Functions

The package currently three main functions: 

- `qmd_to_r()`: Convert a .qmd file into a .R file. Headings are converted into section titles (e.g `# heading -----` as defined by the the shortcut ctrl/cmd + shift + R). Text outside of code chunks is converted into comments. Chunk options defined by `#|` are retained as comments.  
- `r_to_qmd()`: Convert a .R file into a .qmd file. Section titles are converted into headings (e.g `# heading -----` as defined by the the shortcut ctrl/cmd + shift + R). Comments are converted into text in between code chunks (unless the comments are within the code, in which case they stay inside of the code chunk).  
- `knitr_opts_to_yaml()`: Take an existing .rmd file and convert its YAML header options to be compatible with Quarto. Currently minimal functionality. html output options are automatically set to `self-contained: TRUE`. Underscores are replaced with hyphens for all other options.

## Examples

Load `convenr`

```{r eval=FALSE}
library(convertr)
```

Convert Quarto into an R script: 

```{r eval = FALSE}
convertr::qmd_to_r(
  input_dir = "path/to/some_quarto_file.qmd",
  output_dir = "path/to/new_converted_r_script.R"
)
```

Convert an R script into a Quarto file:

```{r  eval = FALSE}
convertr::r_to_qmd(
  input_dir = "path/to/some_R_script.R",
  output_dir = "path/to/new_converted_qmd_file.qmd"
)
```

Convert an RMarkdown chunk options into a Quarto YAML header: 

```{r  eval = FALSE}
convertr::knitr_opts_to_yaml(
  input_dir = "path/to/some_an_old_rmd_file.rmd",
  output_dir = "path/to/new_qmd_file.qmd"
)
```



